Assessing the knowledge of AIDS amongst Women in 1997 Vietnam

### 2022-04-26 outputs/paper/paper.Rmd
update

```{r, echo=FALSE, fig.cap="Supplementary Survey Questions", out.width = '100%'}
knitr::include_graphics(here::here("inputs/data/sta304_diag.jpeg"))
```

@@

# Discussion
The ultimate goal of the paper is to assist policy makers in implementing appropriate and efficient socio-economic policies to help promote the growth of children and reduce infant mortality rate in India. We will first discuss the root of the issue which is the household living environment, women's education and their healthcare decisions which lead them to attend antenatal check-ups. Then, we examine the numerous factors that is affected by conducting antenatal check-ups which include antenatal supplements and birth delivery methods. These factors are one of the few that directly impact the infant mortality rate. Additionally, we also look at the importance of infant's meals in their growth. Lastly, we examine inheritable traits such as anaemia and body weight that could be passed on from mother to child and how they impact the infant mortality rate.

@@

## Body weight of mothers and children and their effect on infant mortality rate

## Anaemia of mothers and children and their effect on infant mortality rate

@@

>>>>

```{r, echo=FALSE, fig.cap="Supplementary Survey Questions", out.width = '100%'}
include_graphics(here::here("inputs/data/sta304_diag.jpeg"))
```

@@

# Discussion
The ultimate goal of the paper is to assist policy makers in implementing appropriate and efficient socio-economic policies to help promote the growth of children and reduce infant mortality rate in India. We will first discuss the root of the issue which is the household living environment, women's education and their healthcare decisions which lead them to attend antenatal check-ups. Then, we examine the numerous factors that is affected by conducting antenatal check-ups which include antenatal supplements and birth delivery methods. These factors are one of the few that directly impact the infant mortality rate. Additionally, we also look at the importance of infant's meals in their growth. Lastly, we examine inheritable traits such as anaemia and body weight that could be passed on from mother to child and how they impact the infant mortality rate. The full data can be found in Appendix B.

@@

## Body weight and anaemia of mothers affecting children and the infant mortality rate
Lastly, we will explore how inheritable traits that mothers possess such as body weight and diseases (anaemia) are inherited by their children and would be detrimental to their health. In our data exploration, women that have BMI below 18.5kg/m

## Summary

@@

# Full data tables
```{r, echo=FALSE, fig.cap="Data Tables", out.width = '100%'}
include_graphics(here::here("inputs/data/factsheet1.png"))
include_graphics(here::here("inputs/data/factsheet2.png"))
include_graphics(here::here("inputs/data/factsheet3.png"))
```
